---
title: "Getting Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, eval = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(seuratTools, lib.loc = "~/rpkgs/devel_install/")
library(seuratTools)
library(tidyverse)
library(Seurat)
library(ggraph)
library(iheatmapr)
library(formattable)
```

# view included dataset 

```{r, eval = TRUE}
seurat_pancreas_reduced

glimpse(seurat_pancreas_reduced)
```

# run clustering on a single seurat object

By default clustering will be run at ten different resolutions between 0.2 and 2.0. Any resolution can be specified by providing the resolution argument as a numeric vector.

```{r}
# debug(stash_marker_features)
debug(getEnrichedPathways)
clustered_seu <- clustering_workflow(seurat_pancreas_reduced, experiment_name = "seurat_pancreas", organism = "human")
```

```{r}
debug(plot_markers)
minimalSeuratApp(clustered_seu)
```

## split included dataset based on collection technology 

```{r}
batches <- seurat_pancreas_reduced %>%
 purrr::map(Seurat::SplitObject, split.by = "dataset") %>%
 purrr::transpose()

names(batches)

glimpse(batches)

```

# run seurat batch integration on 'child' projects

```{r}
integrated_seu <- integration_workflow(batches)
```

# launch app to inspect

```{r}

minimalSeuratApp(integrated_seu)

```

# view analysis details

```{r}
integrated_seu$gene@misc$experiment %>% 
  tibble::enframe() %>% 
  knitr::kable()
```
