---
title: "Preprocessing"
author: 
  - name: Kevin Stachelek
    affiliation:
    - University of Southern California
    email: kevin.stachelek@gmail.com
output: 
  BiocStyle::html_document:
    self_contained: yes
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: show
date: "`r doc_date()`"
package: "`r pkg_ver('chevreul')`"
vignette: >
  %\VignetteIndexEntry{Preprocessing}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}  
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    crop = NULL, ## Related to https://stat.ethz.ch/pipermail/bioc-devel/2020-April/016656.html
    dpi = 900,
    out.width = "100%",
    message = FALSE,
    warning = FALSE
)

library(kableExtra)
library(xfun)

format_table <- function(mydf) {
    
  DT::renderDataTable({
    DT::datatable(mydf,
                  options = list(scrollX = TRUE,...)
                  )      
  })
       mydf
}


chevreul_sce <- chevreuldata::human_gene_transcript_sce()

```

First step is to load Chevreul package and all other packages required 

```{r packages }
devtools::load_all()
library(scran)
library(scuttle)
library(SingleCellExperiment)
library(tidyverse)
library(ggraph)
```

## TLDR

chevreul provides a single command to:

-   construct a SingleCellExperiment object 

-   filter genes by minimum expression and ubiquity

-   normalize and scale expression by any of several methods packaged in SingleCellExperiment



## Set up a object

We start with a gene by cell matrix of count/UMI values and a table of cell metadata

### Matrix containg count values
```{r}
human_count<-counts(chevreul_sce)

human_count[1:5, 1:5]%>%knitr::kable(format = "pipe")
                      
```

### Dataframe containing object metadata
```{r}

human_meta<-colData(chevreul_sce) %>% as.data.frame()
human_meta[1:5,1:5]%>%knitr::kable(format = "pipe")
```

Then using these 2 datasets we can create a SingleCellExperiment object in the usual manner using the `SingleCellExperiment` function

```{r}
myobject <- SingleCellExperiment::SingleCellExperiment(
  assays = list(counts = human_count), 
  colData = human_meta, 
  mainExpName = "gene")
myobject
```

## Preprocess the object

Chevreul includes a handy function `object_preprocess()` that performs standard preprocessing workflow for scRNA-seq data. This function handles normalization and scaling required for downstream data analysis using existing functions. If needed, parameters can be specified by the user.

```{r}
myobject0 <- object_preprocess(myobject)
plotPCA(myobject0, color_by = "nFeature_gene")

```

This single function includes sub-functions that normalize, identify highly variable features and scale the data:

-   First, the sub-function `quickCluster` clusters similar cells based on expression levels, then cell-specific biases are normalized using the `computeSumFactors`, which implements the deconvolution strategy for scaling normalization.

-   After normalization, `modelGeneVar` models the variance of the log-expression profiles for each gene, using this the function `getTopHVGs` identifies top 10% of genes that exhibit high cell-to-cell variation in the dataset.

-   Finally, PCA is performed on the data using the function `runPCA` using subset of top HVG from `getTopHVGs` to remove noise. Then, subset the dimensionality reduction result to the desired number of PCs using `getClusteredPCs`.

### Get a first look at a processed dataset using an interactive shiny app

```{r, eval = FALSE}
minimalSceApp(myobject0)
```

## Perform dimension reduction

Chevreul also includes a separate function `object_reduce_dimentions()` capable of implementing a standardized dimension reduction step to select variable features at a user-specified threshold. This function performs tSNE and UMAP in addition to PCA. The default experiment the dimension reduction is being run on is "gene".

```{r, results=FALSE}
myobject_red <- object_reduce_dimensions(myobject0)
plotUMAP(myobject_red, color_by = "nFeature_gene")
```

This function includes existing object functions which performs dimension reduction techniques. 

## Community detection by clustering

A separate Chevreul function, `object_cluster()`, can be used to perform just the clustering of scRNA-seq data. Here, clustering analysis is performed via Louvain algorithms, using existing functions that perform graph-based clustering. Clustering is performed at a range of resolutions with default value ranging from 0.2 to 2 and PCA reduction.

```{r, results=FALSE, eval=TRUE}
object <- object_cluster(object = myobject0, 
                         resolution = seq(0.2, 2, by = 0.2), reduction = "PCA")
plotPCA(object, color_by = "gene_snn_res.0.2")
```


## `R` session information.

```{r reproduce3, echo=FALSE}
## Session info
library("sessioninfo")
options(width = 120)
session_info()$platform
```
