---
title: "Shiny App"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
    # dev.args = list(png = list(type = "cairo")),
  dpi=900,
  out.width = "100%",
  message = FALSE,
  warning = FALSE
)

library(kableExtra)
```

```{r setup, message = FALSE}
library(chevreul)
library(Seurat)
library(tidyverse)
library(ggraph)
```

## TLDR

chevreul provides a single command to:

-   construct a Seurat object

-   filter genes by minimum expression and ubiquity

-   normalize and scale expression by any of several methods packaged in Seurat

# run clustering on a single seurat object

By default clustering will be run at ten different resolutions between 0.2 and 2.0. Any resolution can be specified by providing the resolution argument as a numeric vector.

```{r, cache = TRUE, eval=FALSE}
clustered_seu <- clustering_workflow(panc8, experiment_name = "seurat_pancreas", organism = "human")
DimPlot(clustered_seu, group.by = "gene_snn_res.0.2")
```

```{r, cache = TRUE, echo=FALSE}
clustered_seu <- readRDS("clustered_seu.rds")
```

# app sections
